Synthesizing Symmetric Lenses

### 2018-07-04 papers/SymmetricLenses/main.tex
add graphs

%Consider the trivial lens
%\lstinline{disc(emp_salary,emp_row,rep(emp_salary),rep(emp_row))}. As this is
%the disconnect lens, the cost of each side is the entropy of the data format, so
%the total cost is $\EntropyOf{\lstinline{emp_salary}} +
%\EntropyOf{\lstinline{emp_row}}$. \lstinline{emp_salary} contains strictly more
%imformation than \EntropyOf{\lstinline{": " . salary}}, and \lstinline{emp_row}
%contains strictly more information than \EntropyOf{\lstinline{": " . salary}},
%so by our metric \lstinline{single_emp_map} is preferable to the disconnect
%lens.
Consider the trivial lens
\lstinline{disc(emp_salary,emp_row,rep(emp_salary),rep(emp_row))}. As this is
the disconnect lens, the cost of each side is the entropy of the data format, so
the total cost is $\EntropyOf{\lstinline{emp_salary} } +
\EntropyOf{\lstinline{emp_row}}$. \lstinline{emp_salary} contains strictly more
information than $\EntropyOf{\lstinline{": " . salary}}$, and
\lstinline{emp_row} contains strictly more information than
\EntropyOf{\lstinline{": " . salary}}, so by our metric
\lstinline{single_emp_map} is preferable to the disconnect lens.
% end overview

@@

    $\REntropyOf{\Regex \Given \InvertOf{\Lens}, \RegexAlt}$
    & =
    & $\LEntropyOf{\Regex \Given \Lens, \RegexAlt}$\\
  \end{tabular}
\end{center}
$\LEntropyOf{\Regex \Given \Lens, \RegexAlt}$ is defined symmetrically.  These
functions calculate the expected number of bits to recover one data format from
a synchronized string in the other format.
The cost of a lens, $c(\Lens \OfType \Regex \Leftrightarrow \RegexAlt) =
\LEntropyOf{\Regex \Given \Lens, \RegexAlt} + \REntropyOf{\RegexAlt \Given
  \Lens, \Regex}$ is the
sum of recovering the left format from the right, and the right from the left.
We have proven theorems demonstrating the calculated entropy corresponds to the
actual conditional entropy to recover the data.\bcp{Again, the proofs should be
  included.}

@@

\paragraph*{Compositional Synthesis} Compositional synthesis allows us to use
previously defined lenses - whether they are previously defined by users or by
synthesis. We alter \GreedySynth such that two regular expression atoms can be
mapped to each other either if they are the same regular expression and have
examples agreeing with the examples\bcp{What does ``have
examples agreeing with the examples'' mean??}, or if there is a lens which is a
composition of predefined lenses between them, where the lens alters the
examples in a desired way.

\paragraph*{\RXSearch Permissiveness Customization}\bcp{I don't follow this:}
While the termination heuristic works for many situations, there are situations
where a large number of expansions must be performed to find the correct lens.
While users could prevent incorrect lenses with a large number of examples, we
find it simpler to let the users specify that \RXSearch should be more
restrictive in which lenses it accepts. If the user's desired transformation has
a particularly high cost, the algorithm may spend a long time searching in vain
for lenses with lower cost.  By tuning \RXSearch to me more permissive in the
lenses it accepts, this search can be short-circuited.
% end synthesis

@@

We have extended Optician\bcp{this is the first mention of the word
  Optician!} with our symmetric synthesis algorithm. Users can 
write synthesis tasks alongside lens combinators, use those synthesis results in
the manual writing of new lenses, and use previously defined lenses in the
synthesis of new lenses.

In this evaluation, we aim to answer two primary questions:
\begin{enumerate}
\item Is our synthesis procedure efficient enough to be used in everyday
  development?  In particular, can it be used in place of the existing
  bijective lens synthesis algorithm integrated with Boomerang (which
  \citet{miltner+:bijective-synthesis} have argued is reasonably fast in
  practice)? 
  \item Are the heuristics we have described useful for reducing the 
  ``specification overhead'' for users?  \bcp{Maybe it would be better to
    ask {\em which} heuristics are the most useful.  Also, are we talking
    about reducing the number of examples needed?  It's not clear.  (And:
    Don't the heuristics also make it faster??)}
\end{enumerate}

\subsection{Benchmark Suite}
Our benchmarks are drawn from four different sources.
\begin{enumerate}
\item We adapted \afm{8} data cleaning benchmarks from Flash Fill. In adopting
  these benchmarks, we go beyond the data cleaning tasks\bcp{confusing: you
    say these are data cleaning tasks, then immediately say we go beyond
    data cleaning tasks.  (I know the next bit of the sentence makes it
    (somewhat) clearer, but the reader is already lost right here.)}, and
  synthesize 
  synchronization functions\bcp{what is a ``synchronization function''}
  between the ad-hoc data and their cleaned forms. 
  Optician also adopted benchmarks from Flash Fill, but required alterations to
  be in bijective form\bcp{Mysterious}. With our symmetric enhancement, we
  \bcp{words missing?} Optician's four 
  benchmarks and 4 new Flash Fill benchmarks with no alterations.
\item We adapted \afm{29} benchmarks from Augeas.  These benchmarks are the same
  as those present in Optician.  While these benchmarks had to be slightly
  adopted for bijectivity, previous work addressed this lack of bijectivity by
  synthesizing quotient bijective lenses~\cite{?}.
\item We used \afm{8} benchmarks from synchronization tasks on synchronizing a
  variety of real-life formats. These formats range from the synchronizing REST
  and JSON web resource descriptions to synchronizing BibTeX and EndNote
  citation descriptions.
\end{enumerate}

\bcp{Why is this a good set of benchmarks for the purposes described earlier
in the section?}

@@

To answer our first research question, we measure the runtime of our algorithm
and compare it to the existing algorithm for synthesizing bijective
lenses.\bcp{Note that this comparison doesn't, directly answer the question
  ``Is it fast enough.''}

@@

\begin{figure}
  \includegraphics{generated-graphs/times}
  \caption{ Number of benchmarks that can be solved by a given algorithm in a
    given amount of time. \SSOpt{} is the full symmetric synthesis algorithm.
    \BSOpt{} is the full bijective lens synthesis algorithm. \SSNCOpt{} is the
    symmetric synthesis algorithm without using a library of existing lenses.
    \BSNCOpt{} is the bijective synthesis algorithm without using a library of
    existing lenses. Our symmetric synthesis algorithm is able to complete all
    benchmarks in our benchmark suite in under 30 seconds, and is able to
    complete most of the benchmarks without using compositional
    synthesis. \bcp{The interesting part of the graph is all squished
      against the Y axis.  Can we make the X axis logarithmic?}}
  \label{fig:times}
\end{figure}

@@

\subsection{The Effect of Our Heuristic}
We evaluate the usefulness of (1) our information theoretic metric, and (2) our
termination heuristic.  To this end, we run our program in 3 different modes:\\
\begin{tabulary}{\linewidth}{rL}
  \NoTPOpt{}: & We synthesize lenses using our symmetric synthesis algorithm,
                but users cannot tune when \RXSearch returns using a termination parameter.\\
  \FCOpt{}: &  The first time \GreedySynth finds a lens, it returns that lens.\\
  \NMCCOpt{}: & The lens cluster that contains is identified through \SSOpt{}. \GreedySynth is then called on that pair of SREs. \\
  \NMOpt{}: & Neither \GreedySynth nor \RXSearch have any notion of cost; they
              both merely search for
              any lens that satisfies the specification. 
\end{tabulary}

\begin{figure}
  \includegraphics{generated-graphs/metrics_importance}
  \caption{Number of benchmarks that synthesize the correct lens by a given
    algorithm. \NoTPOpt{} is the full symmetric synthesis algorithm, but
    termination parameters are ignored. \FCOpt{} provides a notion of cost to
    \GreedySynth, but once a satisfying lens is greedily found, that lens is
    returned. \NMCCOpt{} identifies the lens cluster in which the desired 
    lens lies.  \GreedySynth{} is then run on that cluster with no notion of
    cost. \NMOpt{} removes all notion of cost, and merely finds the first
    satisfying lens.\bcp{Am I reading this wrong, or does even the best
      algorithm fail to find the correct lens something like 20\% of the
      time?!?!?!}} 
  \label{fig:metric}
\end{figure}

>>>>

%Consider the trivial lens
%\lstinline{disc(emp_salary,emp_row,rep(emp_salary),rep(emp_row))}. As this is
%the disconnect lens, the cost of each side is the entropy of the data format, so
%the total cost is $\EntropyOf{\lstinline{emp_salary}} +
%\EntropyOf{\lstinline{emp_row}}$. \lstinline{emp_salary} contains strictly more
%imformation than \EntropyOf{\lstinline{": " . salary}}, and \lstinline{emp_row}
%contains strictly more information than \EntropyOf{\lstinline{": " . salary}},
%so by our metric \lstinline{single_emp_map} is preferable to the disconnect
%lens.
Consider the trivial lens
\lstinline{disc(emp_salary,emp_row,rep(emp_salary),rep(emp_row))}. As this is
the disconnect lens, the cost of each side is the entropy of the data format, so
the total cost is $\EntropyOf{\lstinline{emp_salary} } +
\EntropyOf{\lstinline{emp_row}}$. \lstinline{emp_salary} contains strictly more
imformation than $\EntropyOf{\lstinline{": " . salary}}$, and
\lstinline{emp_row} contains strictly more information than
\EntropyOf{\lstinline{": " . salary}}, so by our metric
\lstinline{single_emp_map} is preferable to the disconnect lens.
% end overview

@@

    $\REntropyOf{\Regex \Given \InvertOf{\Lens}, \RegexAlt}$
    & =
    & $\LEntropyOf{\Regex \Given \Lens, \RegexAlt}$\\
  \end{tabular}
\end{center}
$\LEntropyOf{\Regex \Given \Lens, \RegexAlt}$ is defined symmetrically.  These
functions calculate the expected number of bits to recover one data format from
a synchronized string in the other format.
The cost of a lens, $c(\Lens \OfType \Regex \Leftrightarrow \RegexAlt) =
\LEntropyOf{\Regex \Given \Lens, \RegexAlt} + \REntropyOf{\RegexAlt \Given
  \Lens, \Regex}$ is the
sum of recovering the left format from the right, and the right from the left.
We have proven theorems demonstrating the calculated entropy corresponds to the
actual conditional entropy to recover the data.\bcp{Again, they should be
  included.}

@@

\paragraph*{Compositional Synthesis} Compositional synthesis allows us to use
previously defined lenses - whether they are previously defined by users or by
synthesis. We alter \GreedySynth such that two regular expression atoms can be
mapped to each other either if they are the same regular expression and have
examples agreeing with the examples, or if there is a lens which is a
composition of predefined lenses between them, where the lens alters the
examples in a desired way.

\paragraph*{\RXSearch Permissiveness Customization}
While termination heuristic works for many situations: there are situations
where a large number of expansions must be performed to find the correct lens.
While users could prevent incorrect lenses with a large number of examples, we
find it simpler to let the users specify that \RXSearch should be more
restrictive in which lenses it accepts. If the user's desired transformation has
a particularly high cost, the algorithm may spend a long time searching in vain
for lenses with lower cost.  By tuning \RXSearch to me more permissive in the
lenses it accepts, this search can be short-circuited.
% end synthesis

@@

We have extended Optician with our symmetric synthesis algorithm. Users can
write synthesis tasks alongside lens combinators, use those synthesis results in
the manual writing of new lenses, and use previously defined lenses in the
synthesis of new lenses.

In this work, we aim to answer two primary research questions:
\begin{enumerate}
\item Is our synthesis procedure efficient enough to be used in everyday
  development?  Can it be used in place of the existing bijective lens synthesis
  algorithm integrated with Boomerang?
\item Are our heuristics useful for reducing the specifications users have to
  provide.
\end{enumerate}

\subsection{Benchmark Suite Construction}
Our benchmarks came from four different sources.
\begin{enumerate}
\item We adapted \afm{8} data cleaning benchmarks from Flash Fill. In adopting
  these benchmarks, we go beyond the data cleaning tasks, and synthesize
  synchronization functions between the ad-hoc data and their cleaned forms.
  Optician also adopted benchmarks from Flash Fill, but required alterations to
  be in bijective form. With our symmetric enhancement, we Optician's four
  benchmarks, and 4 new Flash Fill benchmarks with no alterations.
\item We adapted \afm{29} benchmarks from Augeas.  These benchmarks are the same
  as those present in Optician.  While these benchmarks had to be slightly
  adopted for bijectivity, previous work addressed this lack of bijectivity by
  synthesizing quotient bijective lenses~\cite{?}.
\item We used \afm{8} benchmarks from synchronization tasks on synchronizing a
  variety of real-life formats. These formats range from the synchronizing REST
  and JSON web resource descriptions to synchronizing BibTeX and EndNote
  citation descriptions.
\end{enumerate}

@@

To answer our first research question, we analyze the runtime of our algorithm,
and compare it to the existing algorithm for synthesizing bijective lenses.

@@

\begin{figure}
  \includegraphics{generated-graphs/times}
  \caption{ Number of benchmarks that can be solved by a given algorithm in a
    given amount of time. \SSOpt{} is the full symmetric synthesis algorithm.
    \BSOpt{} is the full bijective lens synthesis algorithm. \SSNCOpt{} is the
    symmetric synthesis algorithm without using a library of existing lenses.
    \BSNCOpt{} is the bijective synthesis algorithm without using a library of
    existing lenses. Our symmetric synthesis algorithm is able to complete all
    benchmarks in our benchmark suite in under 30 seconds, and is able to
    complete most of the benchmarks without using compositional synthesis. }
  \label{fig:times}
\end{figure}

@@

\subsection{Heuristic Usefulness}
We evaluate the usefulness of (1) our information theoretic metric, and (2) our
termination heuristic.  To this end, we run our program in 3 different modes:\\
\begin{tabulary}{\linewidth}{rL}
  \NoTPOpt{}: & We synthesize lenses using our symmetric synthesis algorithm,
                but users cannot tune when \RXSearch returns using a termination parameter.\\
  \FCOpt{}: &  The first time \GreedySynth finds a lens, it returns that lens.\\
  \NMCCOpt{}: & The lens cluster that contains is identified through \SSOpt{}. \GreedySynth is then called on that pair of SREs. \\
  \NMOpt{}: & Neither \GreedySynth nor \RXSearch have any notion of cost; they
              both merely search for
              any lens that satisfies the specification. 
\end{tabulary}

\begin{figure}
  \includegraphics{generated-graphs/metrics_importance}
  \caption{Number of benchmarks that synthesize the correct lens by a given
    algorithm. \NoTPOpt{} is the full symmetric synthesis algorithm, but
    termination parameters are ignored. \FCOpt{} provides a notion of cost to
    \GreedySynth, but once a satisfying lens is greedily found, that lens is
    returned. \NMCCOpt{} identifies the lens cluster in which the desired 
    lens lies.  \GreedySynth{} is then run on that cluster with no notion of
    cost. \NMOpt{} removes all notion of cost, and merely finds the first
    satisfying lens.}
  \label{fig:metric}
\end{figure}
